Beam-Helicity and Beam-Charge Asymmetries \\ in the Bethe--Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v2.1)} \underline{Drafting Committee: DC90 (\today)}

### 2012-01-10 theory.tex
Updated with commetns from the DC before christmas

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97a,Rad97} encompass the familiar Parton
Distribution Functions (PDFs) and nucleon Form Factors (FFs) to provide a
comprehensive description of the structure of the nucleon.
Although GPDs are difficult to access experimentally, the {\sc Hermes}
\red{C}ollaboration has previously published results
\cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
the \red{exclusive} leptoproduction of real photons from a nucleon or nucleus that can
be used to constrain GPDs via Compton Form Factors (CFFs). A thorough
description of the nucleon in terms of GPDs would allow the deduction
of the total angular momentum of partons in the nucleon, and the
construction of a longitudinal-momentum-dissected transverse spatial map of parton positions.

Generalised parton distributions depend upon four kinematic variables: the
Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
representing the initial (final) four-momentum of the \red{nucleon}; the average
fraction $x$ of the nucleon's longitudinal momentum carried by the active
quark throughout the scattering process; half the difference of
  the fractions of the nucleon's longitudinal momentum carried
by the active quark at the start and end of the process, written as
the skewness $\xi$; and the square $-Q^2=q^2$ of the four-momentum of
the virtual photon that mediates the lepton-\red{nucleon} scattering
process. In the Bjorken limit of $Q^2\rightarrow\infty$ with fixed
$t$, the skewness $\xi$ is related to the Bjorken variable
$x_{\textrm{B}}=\frac{-q^2}{2p\cdot q}$ as
$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
as a function of $x_{\textrm{B}}$ because there is no consensus on an experimentally observable representation of $\xi$. 
\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[width=0.45\textwidth]{dvcs_both}}
\subfigure[Bethe-Heitler]{\includegraphics[width=0.45\textwidth]{bh_both}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The \red{leading} DVCS process in which an electron/positron ($e$) interacts with a quark in the nucleon
($N$) via a virtual photon ($\gamma^\ast$). The quark is found in the
nucleon with longitudinal momentum fraction $x+\xi$ and emits a real
photon ($\gamma$). The quark is absorbed by the nucleon with
longitudinal momentum fraction $x-\xi$. (b): The \red{leading} Bethe-Heitler process, i.e. the emission of a real photon from the scattering or
scattered lepton. It has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}

Exclusive leptoproduction of real photons
($e\,N\,\rightarrow\,e'\,N'\,\gamma$) arises from
two experimentally indistinguishable processes: the Deeply Virtual Compton Scattering (DVCS) process,
which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-\red{nucleon} scattering with the
emission of a Bremsstrahlung photon by the lepton. \red{The leading terms in these processes are shown in figure~\ref{spin}.}
The BH process is calculable in the QED framework; this process is
dominant at the kinematic conditions of the H{\sc ermes} experiment, but the
scattering amplitudes of the two processes interfere and the large BH amplitude
amplifies the contribution of the DVCS amplitude to the interference term. 
It is through the study of this interference term at H{\sc ermes} that
useful information for the constraint of certain GPDs can be obtained \cite{Bel02b}.

@@

Two sets of asymmetries measured at H{\sc
ermes} with an unpolarised \red{Hydrogen} target and a polarised electron or positron
beam are considered here:
beam-helicity asymmetries and beam-charge asymmetries. This paper,
like ref.~\cite{Air09}, presents results \red{related to} the following asymmetries:
\begin{align}
\hspace{0.5cm}\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} -
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
- \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
&=\dfrac{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=1}^2
s_{n}^{\textrm{I}}\sin(n\phi)}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{
2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)},& 
\label{e:alui}
\end{align}

\begin{align}
\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) -
(\textrm{d}\sigma(\phi)^{+\leftarrow} + 
\textrm{d}\sigma(\phi)^{-\leftarrow})}
{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) +
(\textrm{d}\sigma(\phi)^{+\leftarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}& \nonumber \\[0.4cm]
%\\ \nonumber
&=\dfrac{ K_{\textrm{DVCS}} s_{1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{\, and}&
\label{e:aludvcs}
\end{align}

\begin{align}
\hspace{0.5cm}\mathcal{A}_{\textrm{C}}(\phi) &\equiv  
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&    \nonumber \\
&=\dfrac{{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^3
c_{n}^{\textrm{I}}\cos(n\phi)}}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_
{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)} ,&
\label{e:ac}
\end{align}
where $\textrm{d}\sigma(\phi)^+$ ($\textrm{d}\sigma(\phi)^-$) refers to
cross sections with positive (negative) beam charge and
$\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer\red{s}
to cross sections taken with beam spin parallel (anti-parallel) to the
beam momentum.

\red{The $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{\textrm{I}}$ Fourier
coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
combination of complex Compton Form Factors (CFFs). A CFF is a
convolution of a GPD with a hard scattering kernel. Contributions of
GPDs to the cross section may be relatively suppressed by powers of
$1/Q$, the origin of which may be kinematic in nature or due to the
twist-level of the GPD. Leading twist is twist-2. Typically, the
contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
suppressed by $\mathcal{O}(1/Q^{n-2})$.

\red{T}he leading-twist Fourier coefficients are $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{eqnarray}
s_{1,\textrm{unp}}^{\textrm{I}} \approx&\,\,\,\,8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\textrm{and}&\label{eq:s1}
\\
 c_{1,\textrm{unp}}^{\textrm{I}} \approx&8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,&\label{eq:c1}
\end{eqnarray}
where the definition of the kinematic factor $k$ is found
  in ref.\cite{Bel02b}. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{-t}{4M^2}$ are of order 0.1), the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in eq.~\ref{Eq_cunp} (in first approximation) with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$ can be constrained through
measurements of the $\sin\phi$ and $\cos\phi$ terms of the $\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi)$ and $\mathcal{A}_{\textrm{C}}(\phi)$ asymmetries respectively.}

Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger,
independent data set taken during the years 2006 and 2007 after the
experiment was upgraded in the target region. The work covered
  in this publication combines the data taken in 1996-2005 with this
  new data set to produce the largest DVCS data set that will be published by H{\sc ermes}.
The results in this paper make use of the same missing-mass technique for event selection as was used in ref.~\cite{Air09}.

>>>>

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97a,Rad97} encompass the familiar Parton
Distribution Functions (PDFs) and nucleon Form Factors (FFs) to provide a
comprehensive description of the structure of the nucleon. A thorough
description of the nucleon in terms of GPDs would allow the deduction
of the total angular momentum of partons in the nucleon, and the
construction of a longitudinal-momentum-dissected transverse spatial map of parton positions. \red{There have been several exclusive experimental results that can be used to constrain GPDs, (see \cite{air09}). In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus is the simplest to describe mathematically and is the most widely-used reaction channel for such work.}

Generalised parton distributions depend upon four kinematic variables: the
Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
representing the initial (final) four-momentum of the \red{nucleon}; the average
fraction $x$ of the nucleon's longitudinal momentum carried by the active
quark throughout the scattering process; half the difference of
  the fractions of the nucleon's longitudinal momentum carried
by the active quark at the start and end of the process, written as
the skewness $\xi$; and the square $-Q^2=q^2$ of the four-momentum of
the virtual photon that mediates the lepton-\red{nucleon} scattering
process. In the Bjorken limit of $Q^2\rightarrow\infty$ with fixed
$t$, the skewness $\xi$ is related to the Bjorken variable
$x_{\textrm{B}}=\frac{-q^2}{2p\cdot q}$ as
$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
as a function of $x_{\textrm{B}}$ because there is no consensus on an experimentally observable representation of $\xi$. 
\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[width=0.45\textwidth]{dvcs_both}}
\subfigure[Bethe-Heitler]{\includegraphics[width=0.45\textwidth]{bh_both}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The \red{leading} DVCS process in which an electron/positron ($e$) interacts with a quark in the nucleon
($N$) via a virtual photon ($\gamma^\ast$). The quark is found in the
nucleon with longitudinal momentum fraction $x+\xi$ and emits a real
photon ($\gamma$). The quark is absorbed by the nucleon with
longitudinal momentum fraction $x-\xi$. (b): The \red{leading} Bethe-Heitler process, i.e. the emission of a real photon from the scattering or
scattered lepton. It has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}
Exclusive leptoproduction of real photons
($e\,N\,\rightarrow\,e'\,N'\,\gamma$) arises from
two experimentally indistinguishable processes: the Deeply Virtual Compton Scattering (DVCS) process,
which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-\red{nucleon} scattering with the
emission of a \red{b}remsstrahlung photon by the lepton. \red{The leading terms in these processes are shown in figure~\ref{spin}.}
The BH process is calculable in the QED framework; this process is
dominant at the kinematic conditions of the H{\sc ermes} experiment, but the
scattering amplitudes of the two processes interfere and the large BH amplitude
amplifies \red{the interference term, which is proporional to the DVCS amplitude. At H{\sc ermes} kinematic conditions, it is through the study of this interference term that useful information for the constraint of certain GPDs can be obtained~\cite{Bel02b}, especially since the interference term is the only part of the squared scattering amplitude that is linear in CFFs}.

@@

Two sets of asymmetries measured at H{\sc
ermes} with an unpolarised \red{hydrogen} target and a polarised electron or positron
beam are considered here:
beam-helicity asymmetries and beam-charge asymmetries. This paper,
like ref.~\cite{Air09}, presents results \red{related to} the following asymmetries:
\begin{align}
\hspace{0.5cm}\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} -
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
- \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
&=\dfrac{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=1}^2
s_{\textrm{unp},n}^{\textrm{I}}\sin(n\phi)}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{
2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)},& 
\label{e:alui}
\end{align}

\begin{align}
\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) -
(\textrm{d}\sigma(\phi)^{+\leftarrow} + 
\textrm{d}\sigma(\phi)^{-\leftarrow})}
{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) +
(\textrm{d}\sigma(\phi)^{+\leftarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}& \nonumber \\[0.4cm]
%\\ \nonumber
&=\dfrac{ K_{\textrm{DVCS}} s_{\textrm{unp},1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{\, and}&
\label{e:aludvcs}
\end{align}

\begin{align}
\hspace{0.5cm}\mathcal{A}_{\textrm{C}}(\phi) &\equiv  
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&    \nonumber \\
&=\dfrac{{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^3
c_{\textrm{unp},n}^{\textrm{I}}\cos(n\phi)}}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_
{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)} ,&
\label{e:ac}
\end{align}
where $\textrm{d}\sigma(\phi)^+$ ($\textrm{d}\sigma(\phi)^-$) refers to
\red{the differential} cross section with positive (negative) beam charge and
$\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer\red{s}
to \red{differential} cross section taken with beam spin parallel (anti-parallel) to the
beam momentum.

The $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{\textrm{\red{W}}}$ Fourier
coefficients depend on ``$\mathcal{C}$-functions'' \cite{Bel02b}, each of which is a
combination of complex\red{-valued} Compton Form Factors (CFFs). A CFF is a
\red{flavour-sum of} convolution\red{s} of GPD\red{s} with hard scattering kernel\red{s}. Contributions to the cross section may be relatively suppressed by powers of
$1/Q$, the origin of which may be kinematic in nature or due to the
twist-level of the GPD\red{s appearing in that contribution}. Leading twist is twist-2. Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
suppressed by $\mathcal{O}(1/Q^{n-2})$.

\red{The Fourier coefficients that receive leading-twist contributions are $c_{0,\textrm{unp}}^{\textrm{I}}$, $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. All} of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{eqnarray}
c_{0,\textrm{unp}}^{\textrm{I}} &\approx&-8(2-y)\frac{(2-y^2)}{(1-y)}K^2\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\label{eq:c0}
\\
s_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\textrm{and}\label{eq:s1}
\\
c_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8K(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,.\label{eq:c1}
\end{eqnarray}
\red{The definition of the kinematic factor \red{$K$ is~\cite{Bel02b}}
\begin{equation}
K=\sqrt{\frac{t}{Q^2}\Big(1-\frac{t_{\textrm{min}}}{t}\Big)\Big(1-x_{\textrm{B}}\Big)\Big(1-y-\frac{y^2\epsilon^2}{4}\Big)\Big\lbrace\sqrt{1+\epsilon^2}+\frac{4x_{\textrm{B}}(1-x_{\textrm{B}})+\epsilon^2}{4(1-x_{\textrm{B}})}
\frac{t_{\textrm{min}}-t}{Q^2}\Big\rbrace}
\end{equation} 
where $y$ is the fractional energy transfer from the beam lepton the virtual photon. The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that these amplitudes proportional to these fourier coefficients vanish as $-t$ approaches its minimum value.}
The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  In H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{-t}{4M^2}$ are of order 0.1), the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in eq.~\ref{Eq_cunp} (in first approximation) with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$ can be constrained through
measurements of the $\sin\phi$ and $\cos\phi$ terms of the $\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi)$ and $\mathcal{A}_{\textrm{C}}(\phi)$ asymmetries respectively.

Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 after the
experiment was \red{augmented} in the target region. The work covered
  in this publication combines the data taken in 1996-2005 with this
  new data set to produce the largest DVCS data set that will be published by H{\sc ermes}.
The results in this paper make use of the same missing-mass technique for event selection as was used in ref.~\cite{Air09}.
